Results

### 2020-01-21 analysis/02_analysis.Rmd
Add labels to DAG

```{r causal-dag, fig.width=4.75, fig.height=2}
theory_dag <- dagify(Y ~ I + C + F,
                     C ~ I + F,
                     outcome = "Y",
                     exposure = "C") %>% 
  tidy_dagitty(layout = "sugiyama")

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

>>>>

```{r causal-dag, fig.width=4.75, fig.height=2}
theory_dag <- dagify(Y ~ I + C + F,
                     C ~ I + F,
                     outcome = "Y",
                     exposure = "C",
                     labels = c("Y" = "Outcome (Likelihood of donation & amount donated)", 
                                "C" = "Anti-NGO legal crackdown", 
                                "I" = "NGO issue area", 
                                "F" = "NGO funding source")) %>% 
  tidy_dagitty(layout = "sugiyama")

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  geom_dag_label_repel(aes(label = label), size = pts(6), box.padding = 0.1, 
                       direction = "x", seed = 12345,
                       family = "Roboto Condensed", fontface = "plain") +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())
